Brief Article

### 2012-03-08 power.tex

\section{The Flattening out}
The flattening out in figure \ref{fig:pval_plot_signal} happens, when the signal in the data plot becomes too low to make it distinguishable from a nullplot. 
Under $H_0$ the $p$-value of the data plot $p_B \sim U[0,1]$. If we can assume that an observer is able to pick out the plot corresponding to the minimal $p$-value, we have a distribution of $Beta_{1, m}$ for the picked plot.

>>>>

%\section{The Flattening out}
%The flattening out in figure \ref{fig:pval_plot_signal} happens, when the signal in the data plot becomes too low to make it distinguishable from a nullplot. 
%Under $H_0$ the $p$-value of the data plot $p_B \sim U[0,1]$. If we can assume that an observer is able to pick out the plot corresponding to the minimal $p$-value, we have a distribution of $Beta_{1, m}$ for the picked plot.
